Empty Homes V1

### 2017-06-25 LowUseEngland.Rmd
Bootstrap check for regions
Functionalised the class ratio bootstrap and sreamlined the code so it works nicelu in the regions. The results are looking pretty fire

BarrowCumbriaDATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCumbriaDATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCumbriaDATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()

EdenCumbriaDATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

 ls(pattern = "Cumbria") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG,grepl(paste("Barrow-in-Furness", "Allerdale",
                                    "Carlisle","Copeland","Eden",  
                                    "South Lakeland", sep = "|"), 
                             LAD11NM ) ), 
          filtermap = FALSE,
          title = "Map of Cumbria with all current data")

@@

 ls(pattern = "Cumbria") %>% map_df(~eval(parse(text=.x)))  %>%
corplotter(., "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Cumbria",
           "Low Use Percentage by Ward",
           "Median Price")

@@

@@

>>>>

BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()

EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

 ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG,grepl(paste("Barrow-in-Furness", "Allerdale",
                                    "Carlisle","Copeland","Eden",  
                                    "South Lakeland", sep = "|"), 
                             LAD11NM ) ), 
          filtermap = FALSE,
          title = "Map of Cumbria with all current data")

@@

 ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x)))  %>%
corplotter(., "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Cumbria",
           "Low Use Percentage by Ward",
           "Median Price")

 z1<-   ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)

CumbriaStrap <- ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>%
   DistribCompareBootstrapper(., 1652, 100)

CumbriaStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

 z1<-   ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)

CornStrap<- ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x))) %>%
   DistribCompareBootstrapper(., 1652, 1000)

CornStrap %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

 z1<-   ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)

### 2017-06-25 LowUseLondon.Rmd
Bootstrap check for regions
Functionalised the class ratio bootstrap and sreamlined the code so it works nicelu in the regions. The results are looking pretty fire

test <-  Chelseainfo %>% left_join(., AG)

@@

@@

#%>% setNames(paste0("samp",.x))

@@

```{r}
 ChelPrice <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  select(Admin_ward_code, lsoa11cd, Price =X2) %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F))

ChelseainfoWard <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first))

#bootrapps Chelsea housing stock.
set.seed(16546)
ChelseaWardLowUseStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse), reps = 10000) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  ) %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

ChelseaWardHomesStrap2 <- ClassStrapper(ChelPrice, sum(ChelseainfoWard$WardHomes), 10000)

#bootrapps Chelsea housing stock.
set.seed(16540)
ChelseaWardHomesStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
  map(~ ChelPrice %>% 
        filter(Admin_ward_code == .x) %>% 
  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes), reps = 10000) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  ) %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
         class = fct_relevel(class, "Upper", after = 2)) %>%
select(class, ID, Totals)

test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaWardLowUseStrap1, by = c("class", "ID")) %>%
  rename(LowUse = Totals.y,
         Homes = Totals.x) %>%
  group_by(ID)%>%
  mutate(ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes),
         LowUsePerc = LowUse/sum(LowUse),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse),
         RatioExvsAct = LowUse/ExpectedHomes)

test1 %>% ggplot(., aes(x= class, y = ratio, fill = class)) + geom_boxplot() + 
  labs(title = "Boxplot of bootstrapped Ratios")

test1 %>%
mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
SaveFig("DistributionPlot.png")

>>>>

@@

Chelseainfo %>% filter(LAD11CD =="E09000020") %>%
  BootStrapTtest(.)

@@

@@

```{r}

chelstrap <-  Chelseainfo %>% filter(LAD11CD=="E09000020") %>% 
  DistribCompareBootstrapper(., 1652, 100)

chelstrap %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
SaveFig("DistributionPlot.png")
